---
title: "Week 1"
author: "Mariane Goncalves Kulik"
date: "10/15/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

All coding from the slides...

```{r all, include = TRUE}

library(rethinking)

# ------------ Computing the posterior --

p_grid <- seq(from=0, to=1, length.out = 1000)
prob_p <- rep(1, 1000)
prob_data <- dbinom(6, size=9, prob=p_grid)
posterior <- prob_data*prob_p
posterior <- posterior/sum(posterior)

# ------------ Sampling from the posterior --

samples <- sample(p_grid, prob=posterior, size=1e4, replace=TRUE)

# Percentil intervals (PI): equal area in each tail
PI(samples, prob=.5)
# Highest posterior density intervals (HPDI): narrowest interval containing mass
HPDI(samples, prob=.5)

# ------------ Predictive checks --

nw <- rbinom(1e4, size=9, prob=samples)
                  
```

## Week 1

1. Suppose the globe tossing data had turned out to be 8 water in 15 tosses.
Construct the posterior distribution, using grid approximation. Use the same 
flat prior as before.

```{r ex1}

p_grid <- seq(from=0, to=1, length.out = 1000)
prior <- rep(1, 1000)
prob_data <- dbinom(8, size=15, prob=p_grid)
posterior <- prob_data * prior
posterior <- posterior/sum(posterior)

# He didn't show how to plot yet, so I looked at the solution to know if my results are right:
summary(posterior) # The mean is not even far from 0.53.

```

```{r ex1_check2}

set.seed(100)
samples <- sample(p_grid, prob=posterior, size=1e4, replace=TRUE)
HPDI(samples, prob=.99) # This seams OK - 0.24 to 0.81

```

2. Start over in 1, but now use a prior that is zero below p = 0.5 and a con-
stant above p = 0.5. This corresponds to prior information that a majority
of the Earth’s surface is water. What difference does the better prior make?
If it helps, compare posterior distributions (using both priors) to the true
value p = 0.7.

```{r ex2}

p_grid <- seq(from=0, to=1, length.out = 1000)
prob_p <- c(rep(0, 500), rep(1, 500))   # I modified only the prior here
prob_data <- dbinom(8, size=15, prob=p_grid)
posterior <- prob_data*prob_p
posterior <- posterior/sum(posterior)

#check1
summary(posterior) # Also far from .61

```

```{r ex2_check2}

set.seed(100)
samples2 <- sample(p_grid, prob=posterior, size=1e4, replace=TRUE)
HPDI(samples2, prob=.99) # This seams OK - 0.5 to 0.82

```


```{r ex2_check3}

# Posterior should show more mass around the true p=0.7

dens(samples, xlab="p", xlim=c(0,1), ylim=c(0,6))
dens(samples2, add=TRUE, lty=2)
abline(v=.7, col="red")

```

3. This problem is more open-ended than the others. Feel free to collaborate 
on the solution. Suppose you want to estimate the Earth’s proportion of
water very precisely. Specifically, you want the 99% percentile interval of the
posterior distribution of p to be only 0.05 wide. This means the distance be-
tween the upper and lower bound of the interval should be 0.05. How many
times will you have to toss the globe to do this? I won’t require a precise
answer. I’m honestly more interested in your approach.

```{r ex3}

# Idea 1: Simulate with higher values of N and simulate with predictive checks
# It probably will not work because this approach is more cautious.

# He provided in the solution another valuable info: TRUE p=0.7.
# My approach is not totally wrong, but some changes would be required besides the change in N

set.seed(100)
N <- 20
p_true <- 0.7 
W <- rbinom(1, size=N, prob=p_true)

# This is the same
p_grid <- seq(from=0, to=1, length.out = 1000)
prob_p <- c(rep(0, 500), rep(1, 500))   # I modified only the prior here
prob_data <- dbinom(W, size=N, prob=p_grid)
posterior <- prob_data*prob_p
posterior <- posterior/sum(posterior)

samples3 <- sample(p_grid, prob=posterior, size=1e4, replace=TRUE)

PI99 <- PI(samples, .99)
as.numeric(PI99[2]-PI99[1])

```